Death By Dropdown?

### 2025-04-03 conference-materials/2025_shiny-conf/slides.qmd
Updates bidux snippet
- Enhances example to demonstrate bidux Phase 1 features, including fuzzy search and case-insensitive lookup in the concept dictionary.
- Introduces automatic theory suggestions and a piped workflow for BID stage documentation, highlighting improvements in user guidance and UI recommendations.
- Aims to provide practical insights into bidux usage for ShinyConf 2025.

```r
library(bidux)

# concept dictionary functionality
processing_fluency <- bid_concept("processing fluency")
print(processing_fluency)

# BID stage documentation functionality (piped workflow)
project_docs <- bid_notice(
  problem = "users overwhelmed by filtering options", 
  theory = "cognitive load theory", # use if wanting to apply specific concept; leave blank if unsure
  evidence = c("user feedback results", "dashboard telemetry data")
) |>
  bid_interpret(
    central_question = "How to simplify?",
    data_story = list(hook = "Too complex", context = "Many tabs")
  )
print(project_docs)
```

@@

::: {.notes}
**Code Example**: Show practical usage of the package.

- "The concept dictionary gives you instant access to behavioral principles"
  * "Each concept includes definition, code examples, and empirical evidence"
- "The stage documentation functions help structure your design thinking"
  * "These functions are designed to work together via pipes (cf, tidyverse)"
- "Documentation becomes part of your development process, not separate"
- Point out the commented future code to generate excitement
- "In Phase 2, you'll be able to ..."
- When the link appears: "We're launching this at ShinyConf today - check out the repo"
:::

>>>>

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: "1-2|4-6|8-13|14-24|25-28|30-31|32|33"

# Concept dictionary with fuzzy searching and case-insensitive lookup
bid_concept("processing fluency")

# Search for concepts across UI/UX, psychology, and data viz domains
viz_concepts <- bid_concepts("visual") 
paste("Found", nrow(viz_concepts), "visualization-related concepts")

# BID stage documentation and guided suggestions
project_docs <- bid_notice(
  problem = "Users overwhelmed by filtering options and dropdown menus",
  # Theory parameter is optional - will auto-suggest appropriate theory if empty
  evidence = "Feedback shows 65% of users abandon the dashboard after first use"
) |>
  bid_interpret(
    central_question = "How can we simplify the filtering experience?",
    # More details are better, but the function will offer suggestions if needed
    data_story = list(
      hook = "Dashboard abandonment hurts decision-making",
      context = "Current UI requires too many decisions before seeing results",
      resolution = "Simplify filter UI with smart defaults",
      audience = "Marketing team",
      metrics = c("Time to insight", "Filter usage")
    )
  ) |>
  bid_structure(
    layout = "dual_process",
    concepts = c("Principle of Proximity", "Default Effect")
  )

# Get component suggestions based on your BID analysis
ui_suggestions <- bid_suggest_components(project_docs, package = "bslib")
ui_suggestions$component[1]
ui_suggestions$description[1]
```

@@

::: {.notes}
**Code Example**: {bidux} introduction

- Let's look at our Phase 1 implementation of the {bidux} package, which we're releasing today.
- The concept dictionary provides case-insensitive lookups with implementation tips - not just theory, but practical advice on applying each concept.
- You can search across psychology, UI/UX, and data visualization concepts to find what's most relevant to your problem.
- The core of the package is a pipeline of functions that guide you through the 5 BID stages:
  * `bid_notice()` now auto-suggests appropriate theories based on your problem description
  * `bid_interpret()` helps structure your data story with enhanced details
  * `bid_structure()` documents your layout decisions and related concepts
  * Each function provides helpful suggestions as you work
- When we add the upcoming component suggestion system, you'll get tailored UI recommendations based on your BID analysis - showing exactly how to implement these principles in your Shiny code.
- This is just Phase 1 - in Phases 2-4, we'll be adding LLM integration and ready-to-use UI components.
- When the link appears: "We're launching this at ShinyConf today - check out the repo"
:::
